A Taxonomy of Twists of Supersymmetric Yang--Mills Theory

### 2020-02-22 paper.tex
typo fix

The last term $S^{(2)}(tQ_1 + sQ_2)$ in Equation (\ref{eqn:(2,1)2}) is proportional to $\Tilde{\chi}^*$, therefore it disappears upon applying the third step above. 
Applying all the remaining steps, the first term $S(s,0)$ becomes the action functional of the $(1,1)$ twist upon setting $s=1$, see Theorem \ref{thm:4d4partialtwist}. 
Finally, the term in parentheses in Equation (\ref{eqn:(2,1)2}) agrees with the $t$-dependent terms of in Equation (\ref{eqn:(2,0)}), (accept now the fields are adjoint valued). 
We have already seen that the $t$-dependent terms give rise to the desired Hodge family, so this completes the proof. 
\end{proof}

>>>>

The last term $S^{(2)}(tQ_1 + sQ_2)$ in Equation (\ref{eqn:(2,1)2}) is proportional to $\Tilde{\chi}^*$, therefore it disappears upon applying the third step above. 
Applying all the remaining steps, the first term $S(s,0)$ becomes the action functional of the $(1,1)$ twist upon setting $s=1$, see Theorem \ref{thm:4d4partialtwist}. 
Finally, the term in parentheses in Equation (\ref{eqn:(2,1)2}) agrees with the $t$-dependent terms of in Equation (\ref{eqn:(2,0)}), (where now the fields are adjoint valued). 
We have already seen that the $t$-dependent terms give rise to the desired Hodge family, so this completes the proof. 
\end{proof}
